GeoSPARQL 1.1: an almost decadal update to the most important geospatial LOD standard

### 2021-03-10 manuscript.tex
fix authors & package clashes

\usepackage{graphicx}
\usepackage{todonotes}
\usepackage{listingsutf8}
\usepackage{cleveref}
\usepackage[hidelinks]{hyperref,xcolor}
\renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\author{
    Nicholas J. Car\inst{1,2}\orcidID{0000-0002-8742-7730} \and \\
    Timo Homburg\inst{3}\orcidID{0000-0002-9499-5840} % \and \\
    % Third Author\inst{3}\orcidID{2222-3333-4444-5555}
}

@@

\institute{SURROUND Australia Pty Ltd., Brisbane Australia \and
Australian National University, Canberra Australia \and Mainz University Of Applied Sciences, Germany
\email{nicholas.car@surroundaustralia.com, timo.homburg@hs-mainz.de}\\
\url{https://surroundaustralia.com} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}

>>>>

\usepackage{graphicx}
\usepackage{todonotes}
\usepackage{listingsutf8}
\usepackage[hidelinks]{hyperref}
\usepackage{cleveref}

\renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\author{
    Nicholas J. Car\inst{1}\orcidID{0000-0002-8742-7730} \and \\
    Timo Homburg\inst{2}\orcidID{0000-0002-9499-5840} \and \\
    Simon J.D Cox\inst{3}\orcidID{0000-0002-3884-3420}
}

@@

\institute{
    {
    SURROUND Australia Pty Ltd., Australia \&\\
    Australian National University, Australia\\
    \email{nicholas.car@surroundaustralia.com}\\
    \url{https://surroundaustralia.com}
    }
    \and
    {
        Mainz University Of Applied Sciences, Germany\\
        \email{timo.homburg@hs-mainz.de}
    }
    \and 
    {
        Commonwealth Scientific \& Industrial Research Organisation, Australia\\
        \email{simon.cox@csiro.au}
    }
}
